---
title: "R Notebook"
output: html_notebook
---

# Chapter 2 - Names and values

## 2.2 Binding basics
```{r 01}
library(lobstr)
library(tidyverse)
x <- c(1, 2, 3)
obj_addr(x)
y <- x
obj_addr(y)
```

### 2.2.2 Exercises
```{r 2.2.2.1}
a <- 1:10
b <- a
c <- b
d <- 1:10
```

```{r}
obj_addr(a)
obj_addr(b)
obj_addr(c)
obj_addr(d)
```

```{r 2.2.2.2}
obj_addr(mean)
obj_addr(base::mean)
obj_addr(get("mean"))
obj_addr(evalq(mean))
obj_addr(match.fun("mean"))
```

```{r}
mean_functions <- list(mean,
                       base::mean,
                       get("mean"),
                       evalq(mean),
                       match.fun("mean"))

unique(obj_addrs(mean_functions))
#> [1] "0x2fdf308"
```

```{r 2.2.2.3}
example2223 <- tibble(
  `if` = c(1,2,3),
  `_1234` = c(4,5,6),
  `column 1` = c(7,8,9)
)

write.csv(example2223, "example2223.csv", row.names = FALSE)
```

Import using adjusted column names to be syntactically valid:
```{r}
read.csv(file = "example2223.csv", check.names = TRUE)
```

Import using non-adjusted column names:
```{r}
read.csv(file = "example2223.csv", check.names = FALSE)
```

Import using tidyverse where names are not adjusted:
```{r}
df_non_syntactic_name <- read_csv(file = "example2223.csv")
```

```{r}
df_non_syntactic_name$if
```

```{r}
df_non_syntactic_name$`if`
```

```{r}
df_non_syntactic_name %>% select(`if`)
```
```{r}
df_non_syntactic_name["if"]
```

```{r}
df_non_syntactic_name[`if`]
```

"The easiest way to think about this is that backticks refer to objects while quotation marks refer to strings. dplyr::select() accepts object references as well as string references, while base R subsetting is done with a string or integer position."

## 2.3 Copy-on-modify
```{r}
x <- c(1,2,3)
y <- x

y[[3]] <- 4
x
y
```

### 2.3.1 `tracemem()`
```{r}
x <- c(1, 2, 3)
cat(tracemem(x), "\n")
```
```{r}
y <- x
y[[3]] <- 4L
```
```{r}
y[[3]] <- 5L
obj_addr(x)
obj_addr(y)

untracemem(y)
```

### 2.3.2 Function calls
```{r}
f <- function(a) {
  a
}

x <- c(1,2,3)
cat(tracemem(x), "\n")
    
z <- f(x)

untracemem(x)
```

### 2.3.3 Lists
```{r}
l1 <- list(1,2,3)
l2 <- l1
l2[[3]] <- 4

ref(l1, l2)
```

### 2.3.6 Exercises
```{r 2.3.6.1}
tracemem(1:10)
```
```{r 2.3.6.2}
x <- c(1L, 2L, 3L)
tracemem(x)

x[[3]] <- 4

typeof(x)

x <- 1:3
typeof(x)
tracemem(x)
x[[3]] <- 4L

```

```{r 2.3.6.3}
a <- 1:10
b <- list(a, a)
c <- list(b, a, 1:10)
ref(a)
ref(b)
ref(c)
```

```{r 2.3.6.4}
x <- list(1:10)
x
ref(x)
x[[2]] <- x
x
ref(x)
str(x)
```

```{r}
l1 <- list(1,2,3)
l2 <- l1
ref(l1)
ref(l2)

```
```{r}
obj_addr(l1)
obj_addr(l1[[1]])
obj_addr(l2[[1]])
```
```{r}
l1
l1[1]
l1[[1]]
obj_addr(l1[1])
ref(l1[1])
identical(obj_addr(l1[1]), obj_addr(l2[1]))
```
This is because using singular brackets wraps the value 1 in a new list that is created on the fly which will have a unique address. We can use double brackets to confirm our mental model that the sublists are also identical:
```{r}
identical(obj_addr(l1[[1]]), obj_addr(l2[[1]]))
```

## 2.4 Object size
```{r}
obj_size(letters)

x <- runif(1e6)
obj_size(x)

y <- list(x,x,x)
obj_size(y)

obj_size(x, y)
```

```{r}
obj_size(1:3)
obj_size(1:1e3)
obj_size(1:1e6)
obj_size(1:1e9)
```

### 2.4.1 Exercises
```{r 2.4.1.1}
y <- rep(list(runif(1e4)), 100)
object.size(y)
obj_size(y)
```
`object.size()` doesn’t account for shared elements within lists. Therefore, the results differ by a factor of ~ 100.

```{r 2.4.1.2}
funs <- list(mean, sd, var)
obj_size(funs)
```

```{r 2.4.1.3}
a <- runif(1e6)
obj_size(a)

b <- list(a, a)
obj_size(b)  #size of a plus 80
obj_size(a, b) # size of b alone

b[[1]][[1]] <- 10
obj_size(b) # twice previous size of b
obj_size(a, b) # size of new b

b[[2]][[1]] <- 10
obj_size(b) # same as previous new b
obj_size(a, b) # b no longer shares a reference to a, so we add a and b up
```

## 2.5 Modify-in-place
### 2.5.1 Ojbects with a single binding
```{r}
x <- data.frame(matrix(runif(5 * 1e4), ncol = 5))
medians <- vapply(x, median, numeric(1))
cat(tracemem(x), "\n")

for (i in seq_along(medians)) {
  x[[i]] <- x[[i]] - medians[[i]]
}

untracemem(x)
```

```{r}
y <- as.list(x)
cat(tracemem(y), "\n")

for (i in 1:5) {
  y[[i]] <- y[[i]] - medians[[i]]
}
```

### 2.5.3 Exercises
```{r 2.5.3.1}
x <- list()
x[[1]] <- x
```

```{r 2.5.3.2}
create_random_df <- function(nrow, ncol) {
  random_matrix <- matrix(runif(nrow * ncol), nrow = nrow)
  as.data.frame(random_matrix)
}

subtract_medians <- function(x, medians){
  for (i in seq_along(medians)) {
    x[[i]] <- x[[i]] - medians[[i]]
  }
  x
}

subtract_medians_l <- function(x, medians){
  x <- as.list(x)
  x <- subtract_medians(x, medians)
  as.data.frame(x)
}
```




















