---
title: "R Notebook"
output: html_notebook
---

# Chapter 3 - Vectors

## 3.2 Atomic vectors
### 3.2.5 Exercises
```{r 3.2.5.1}
?raw
xx <- raw(2)

```

```{r 3.2.5.2}
c(1, FALSE)
c("a", 1)
c(TRUE, 1L)

```

```{r 3.2.5.3}

```

## 3.3 Attributes
```{r}
a <- 1:4
attr(a, "x") <- "abcdef"
attr(a, "x")

attr(a, "y") <- 4:6
str(attributes(a))

a <- structure(
  1:4,
  x = "abcdef",
  y = 4:6
)
str(attributes(a))
```

### 3.3.4 Exercises
```{r 3.3.4.1}
setNames
unname
```

```{r 3.3.4.2}
x <- 1:10
# return NULL
nrow(x)
#> NULL
ncol(x)
#> NULL

# Pretend it's a column-vector
NROW(x)
#> [1] 10
NCOL(x)
#> [1] 1
```

```{r 3.3.4.3}
x1 <- array(1:5, c(1, 1, 5))  # 1 row,  1 column,  5 in third dimension
x2 <- array(1:5, c(1, 5, 1))  # 1 row,  5 columns, 1 in third dimension
x3 <- array(1:5, c(5, 1, 1))  # 5 rows, 1 column,  1 in third dimension
```

```{r 3.3.4.4}
structure(1:5, comment = "my attribute")
#> [1] 1 2 3 4 5
```

Contrary to other attributes, the comment is not printed (by print or print.default).

```{r}
foo <- structure(1:5, comment = "my attribute")

attributes(foo)
#> $comment
#> [1] "my attribute"
attr(foo, which = "comment")
#> [1] "my attribute"
```

### 3.4.1 FActors
```{r}
x <- factor(c("a", "b", "b", "a"))
x

typeof(x)
attributes(x)
```

```{r}
grade <- ordered(c("b", "b", "a", "c"), levels = c("c", "b", "a"))
grade
```

### 3.4.5 Exercises
```{r 33.4.5.1}
x <- sample(1:10, 1e4, replace = TRUE)
y <- table(x)
y
typeof(y)
attributes(y)

x <- table(mtcars[c("vs", "cyl", "am")])
x
levels(mtcars$am)
mtcars$am
```

```{r 3.4.5.2}
f1 <- factor(letters)
f1
as.integer(f1)
levels(f1) <- rev(levels(f1))
f1
as.integer(f1)
```
The underlying integer values stay the same, but the levels are changed, making it look like the data as changed.

```{r 3.4.5.3}
f2 <- rev(factor(letters)) # reverses element order (only)
f3 <- factor(letters, levels = rev(letters))  # reverses factor level order (only)

f2
f3

```
For f2 and f3 either the order of the factor elements or its levels are being reversed. For f1 both transformations are occurring.


## 3.6 Data frames and tiblles
### 3.6.6 LIst columns
```{r}
df <- data.frame(x = 1:3)
df$y <-  list(1:2, 1:3, 1:4)
df

data.frame(
  x = 1:3, 
  y = I(list(1:2, 1:3, 1:4))
)

df$y[1]
```

```{r}
library(tibble)
tibble(
  x = 1:3,
  y = list(1:2, 1:3, 1:4)
)
```

### 3.6.8 Exercises
```{r 3.6.8.1}
df <- data.frame()
df
```

```{r 3.6.8.2}
df <- data.frame(x = 1:3)
# row.names(df) <- c("x", "y", "y")

row.names(df) <- c("x", "y", "z")
df[c(1, 1, 1), , drop = FALSE]
#>     x
#> x   1
#> x.1 1
#> x.2 1

df[c(1,1,1),]
```
